### 2019-04-22 dantzig_selector/report/4_simulation.tex
Kronecker product identity proof
Helper functions

\Result
{Definition}
{
For \m {x \in \Mb {V} \SB {M}}, we say that \m {\Mc {R} \SB {x}} is the real representation of \m {x}, defined by
%
\Disp {
\NC \Mc {R} \SB {x} \in \NC \Mb {V} \SB {2M} \NR[+]
\NC \Mc {R} \SB {x} \DB {m} =
\NC \startcases
\NC \Mf {Re} \SB {x \DB {m'}}, \MC m =2m' \NR
\NC \Mf {Im} \SB {x \DB {m'}}, \MC m =2m'+1 \NR
\stopcases \NR[+]
\NC m' \NC =  1, \dots, M \NR
}
%
}

@@

\Result
{Definition}
{
For \m {A \in \Mb {M}_{\Mb {C}} \SB {M_1, M_2}}, we say that \m {\Mc {R} \SB {A}} is the real representation of \m {A}, defined by
%
\Disp {
\NC \Mc {R} \SB {A} \in \NC \Mb {M}_{\Mb {R}} \SB {2M_1, 2M_2} \NR[+]
\NC \Mc {R} \SB {A} \DB {m_1,m_2} =
\NC \startcases
\NC \Mf {Re} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
\NC \Mf {Im} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
\NC -\Mf {Im} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
\NC \Mf {Re} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
\stopcases \NR[+]
\NC m_1' \NC = 1, \dots, M_1 \NR
\NC m_2' \NC = 1, \dots, M_2 \NR
}
%
}

@@

%
\Disp {
\NC \T {\V {y}}
\NC = \Mc {R} \SB {\V {y}}
\in \Mb {V}_{\Mb {R}} \SB {2N_y} \NR[+]
\NC \T {\V {g}}
\NC = \Mc {R} \SB {\V {g}}
\in \Mb {V}_{\Mb {R}} \SB {2N_h} \NR[+]
\NC \T {\M {P}}
\NC = \Mc {R} \SB {\M {P}}
\in \Mb {M}_{\Mb {R}} \SB {2N_y, 2N_h} \NR[+]
\NC \T {\V {z}}
\NC = \Mc {R} \SB {\V {z}} \in \Mb {V}_{\Mb {R}} \SB {2N_y} \NR[+]
}
%
such that, by construction,
%
\Disp {
\NC \V {\T {y}} \NC = \M {\T {P}} \V {\T {g}} +\V {\T {z}}
}
%

@@

%
\Disp {
\NC {\V {u}}_{n_h}^{(h)} \in \NC \Mb {V}_{\Mb {R}} \SB {N_h} \NR[+]
\NC {\V {u}}_{n_h}^{(h)} \DB {n_h'}
\NC =
\startcases
1, \quad \MC n_h' =n_h \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC {\T {\M {U}}}_{n_h}^{(h)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR[+]
\NC {\T {\M {U}}}_{n_h}^{(h)} \DB {n_h', n_h''}
\NC =
\startcases
1, \quad \MC n_h' =2n_h -1,\; n_h'' =2n_h -1 \NR
1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h -1 \NR
1, \quad \MC n_h' =2n_h -1,\; n_h'' =2n_h \NR
1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC n_h, n_h', n_h'' \NC = 1, \dots, N_h \NR
}
Moreover, denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
Now, if we introduce vector \m{\V{m}}

\Disp{
\NC \V {m} \NC \in \Mb {V}_{\Mb {R}} \SB {N_h} \NR[+]
\NC \V{m} \DB{n_h}
\NC =\Nm{\V{g} \DB{n_h}} \NR[+]
\NC n_h, n_h', n_h'' \NC = 1, \dots, N_h \NR
}

@@

\Disp{
\NC \V{t}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR[+]
\NC \V{x}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR[+]
\NC \M{A}_i
\NC \in \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_y +N_h} \NR[+]
\NC \V{b}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR[+]
\NC \V{c}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_h} \NR[+]
\NC d_i
\NC \in \Mb {R} \NR[+]
}

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_y}}, \m{\g \geq 0}.
\item Define \m{\V{t}, \V{x}, \M{A}_i, \V{b}_i, \V{c}_i, d_i} according to ().
\item Calculate
\Disp{
\NC \Hat {\V {x}}
\NC = \startcases
\NC \Min {\V {x}' \in \Mb {V}_{\Mb {C}} \SB {N_h}}
\MC \IP {\V {t}, \V {x}'} \NR[+]
\NC \Mr {subject} \; \Mr {to}
\quad  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
\leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
\NC \MC i =1, 2, \dots, N_y +N_h \NR
\stopcases \NR[+]
}
\item Extract
\Disp{
\NC \Hat{\T{\V{g}}} =\NC \Hat{\V{x}} \DB {1 : 2N_h} \NR[+]
}
\item Convert 
\Disp{
\NC \Hat{\V{g}} =\NC \Mc{R} ^{-1} \SB {\Hat{\T{\V{g}}}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {G} =\Mr {vec}^{-1} \SB {\Hat {g}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {\M {H}} =\M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}

>>>>

\Result
{Definition}
{
For \m {x \in \Mb {V} \SB {M}}, we say that \m {\Mc {R} \SB {x}} is the real representation of \m {x}, defined by
%
\Disp {
\NC \Mc {R} \SB {x}
\in \NC \Mb {V} \SB {2M} \NR
\NC \Mc {R} \SB {x} \DB {m} =
\NC \startcases
\NC \Mf {Re} \SB {x \DB {m'}}, \MC m =2m' \NR
\NC \Mf {Im} \SB {x \DB {m'}}, \MC m =2m'+1 \NR
\stopcases \NR[+]
\NC m' \NC =  1, \dots, M \NR
}
%
}

@@

\Result
{Definition}
{
For \m {A \in \Mb {M}_{\Mb {C}} \SB {M_1, M_2}}, we say that \m {\Mc {R} \SB {A}} is the real representation of \m {A}, defined by
%
\Disp {
\NC \Mc {R} \SB {A}
\in \NC \Mb {M}_{\Mb {R}} \SB {2M_1, 2M_2} \NR
\NC \Mc {R} \SB {A} \DB {m_1,m_2} =
\NC \startcases
\NC \Mf {Re} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
\NC \Mf {Im} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
\NC -\Mf {Im} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
\NC \Mf {Re} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
\stopcases \NR[+]
\NC m_1' \NC = 1, \dots, M_1 \NR
\NC m_2' \NC = 1, \dots, M_2 \NR
}
%
}

@@

%
\Disp {
\NC \T {\V {y}}
\in \NC \Mb {V}_{\Mb {R}} \SB {2N_y} \NR
\NC \T {\V {y}}
\NC = \Mc {R} \SB {\V {y}} \NR[+]
\NC \T {\V {g}}
\in \NC \Mb {V}_{\Mb {R}} \SB {2N_h} \NR
\NC \T {\V {g}}
\NC = \Mc {R} \SB {\V {g}} \NR[+]
\NC \T {\M {P}}
\in \NC \Mb {M}_{\Mb {R}} \SB {2N_y, 2N_h} \NR
\NC \T {\M {P}}
\NC = \Mc {R} \SB {\M {P}} \NR[+]
\NC \T {\V {z}}
\in \NC \Mb {V}_{\Mb {R}} \SB {2N_y} \NR
\NC \T {\V {z}}
\NC = \Mc {R} \SB {\V {z}} \NR[+]
}
%
such that, by construction,
%
\Disp {
\NC \V {\T {y}} \NC = \M {\T {P}} \V {\T {g}} +\V {\T {z}}
}
%

@@

%
\Disp {
\NC {\V {u}}_{n_h}^{(h)} \in \NC \Mb {V}_{\Mb {R}} \SB {N_h} \NR
\NC {\V {u}}_{n_h}^{(h)} \DB {n_h'}
\NC =
\startcases
1, \quad \MC n_h' =n_h \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC {\T {\M {U}}}_{n_h}^{(h)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR
\NC {\T {\M {U}}}_{n_h}^{(h)} \DB {n_h', n_h''}
\NC =
\startcases
1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h \NR
1, \quad \MC n_h' =2n_h +1,\; n_h'' =2n_h \NR
1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h +1 \NR
1, \quad \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC n_h, n_h', n_h'' \NC = 0, \dots, N_h -1 \NR
}
Moreover, denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
Now, if we introduce vector \m{\V{m}}

\Disp{
\NC \V {m} \NC \in \Mb {V}_{\Mb {R}} \SB {N_h} \NR
\NC \V{m} \DB{n_h}
\NC =\Nm{\V{g} \DB{n_h}} \NR[+]
\NC n_h, n_h', n_h'' \NC = 0, \dots, N_h -1 \NR
}

@@

\Disp{
\NC \V{t}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR
\NC \V{x}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR
\NC \M{A}_i
\NC \in \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_y +N_h} \NR
\NC \V{b}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR
\NC \V{c}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_h} \NR
\NC d_i
\NC \in \Mb {R} \NR
}

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_y}}, \m{\g \geq 0}.
\item Define \m{\V{t}, \V{x}, \M{A}_i, \V{b}_i, \V{c}_i, d_i} according to ().
\item Calculate
\Disp{
\NC \Hat {\V {x}}
\NC = \startcases
\NC \Min {\V {x}' \in \Mb {V}_{\Mb {C}} \SB {N_h}}
\MC \IP {\V {t}, \V {x}'} \NR[+]
\NC \Mr {subject} \; \Mr {to}
\quad  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
\leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
\NC \MC i =1, 2, \dots, N_y +N_h \NR
\stopcases \NR[+]
}
\item Extract
\Disp{
\NC \Hat{\T{\V{g}}} =\NC \Hat{\V{x}} \DB {1 : 2N_h} \NR[+]
}
\item Convert 
\Disp{
\NC \Hat{\V{g}} =\NC \Mc{R} ^{-1} \SB {\Hat{\T{\V{g}}}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {G} =\NC \Mr {vec}^{-1} \SB {\Hat {g}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {\M {H}} =\NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}
